Using simulation to optimize the sampling design of fisheries-independent trawl surveys

### 2018-09-06 analysis/presentation/sim_survey_presentation.Rmd
Refine presentation

<font size="8"> &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 1 </font> | <font size="8"> &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 2 </font> | <font size="8"> &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 3 </font>
:----: | :----: | :----:
Conduct sets at multiple locations | Sub-sample catch for length measurements | Sub-sampling length groups for age determination
<img src="graphics/trawl_survey_crop.jpg" height="180"/> | <img src="graphics/cod_length.jpg" height="120"/> | <img src="graphics/Otoliths2_crop.jpg" height="140"/>

@@

@@

>- Increases in secondary sampling does little to improve estimates
>- Bias is negligible in this scenario

@@

- With age-specific clustering, fish of different ages are not encountered with equal probability
    - A survey with few sets will be less likely to encounter groups in a tight cluster
        - Survey-level length / age distribution ∴ more likely to be incomplete 
            - Increasing length / age sampling cannot improve perception of the population-level distribution

## Interpretation {.tighter .smaller}

Ages caught and sampled in year 18 from one survey scenario:

>- $D_{sets} = 0.002, M_{lengths} = 500, M_{ages} = 10$

<dev class = "left">
```{r, fig.height = 4.8}

samp <- merge(main_sim$setdet, main_sim$samp, by = "set")
samp <- samp[sim == 1 & year == 18, ]
caught <- as.data.frame(table(samp$age))
caught <- data.frame(group = "Caught", age = caught$Var1, freq = caught$Freq,
                     prop = caught$Freq / sum(caught$Freq))
measured <- as.data.frame(table(samp$age[samp$measured]))
measured <- data.frame(group = "Sampled", age = measured$Var1, freq = measured$Freq,
                       prop = measured$Freq / sum(measured$Freq))
true <- data.frame(group = "True", age = sim$ages, freq = sim$I[, 1],
                   prop = sim$I[, 1] / sum(sim$I[, 1]))
d <- rbind(caught, measured, true)

plot_ly(data = d) %>% 
  add_lines(x = ~age, y = ~prop, color = ~group,
            colors = rev(viridis::viridis(3))) %>% 
  tight_layout(xaxis = list(title = "Age"),
               yaxis = list(title = "Proportion"),
               margin = list(r = 60))

```
</dev>

@@

- Large catches are relatively infrequent
    - Samples in large sets are not independent
        - If the goal is to maximize information, it is likely better to stop collecting psudoreplicates and, instead, focus efforts on other species or the next set

>>>>

<font size="8"> &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 1 </font> | <font size="8"> &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 2 </font> | <font size="8"> &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 3 </font>
:----: | :----: | :----:
Conduct sets at multiple locations | Sub-sample catch for length measurements | Sub-sample length groups for age determination
<img src="graphics/trawl_survey_crop.jpg" height="180"/> | <img src="graphics/cod_length.jpg" height="120"/> | <img src="graphics/Otoliths2_crop.jpg" height="140"/>

@@

## Simulation steps {.smaller}

1. **Simulate abundance**
    - Common cohort model
2. **Simulate spatial aggregation**
    - Includes depth associations and noise correlated across space, years and ages
3. **Simulate surveys**
    - Stratified random surveys with different sampling protocol
5. **Analyze**
    - Conduct stratified analyses and compare <a href="javascript:slidedeck.loadSlide(20)">truth vs. estimate</a>

@@

>- Bias is negligible in this scenario
>- Increases in secondary sampling does little to improve estimates

@@

- Likely related to age-specific clustering
- Alternate analyses (e.g. ogmap, geostatistical models) may be able to account for such clustering and, therefore, provide estimates with less bias
- Requires further investigation

@@

- Large catches are relatively infrequent and samples in these sets are not independent
- If the goal is to maximize information, it is likely better to stop collecting psudoreplicates and, instead, focus efforts on other species or the next set
